---
title: "Hadley3.3-3.6"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```


## Easy Level

### Exercise 1

*Here's a simple exercise with an empty code chunk provided for entering the answer.*

First Let's try making facets for our mpg data. Use facet_wrap on any one categorical variable & facet_grid on any two categorical variable. Can you see the difference?
```{r Facet, exercise=TRUE}

```

### Exercise 2

*Labeling is important for both the analyst and for those who use those visualizations*

Let's label the facets we made by putting lab() function
```{r Labeling, exercise=TRUE}

```

## Intermediate level

### Exercise 3

*Where do we use geom_smooth? A linear model can be created on a scatterplot by using this which will be the 'best fit' line or a line average of all the points.*

For the air quality dataset, given the scatterplot, find the 'best fit' line:

```{r airquality, exercise=TRUE, exercise.eval=TRUE}
library(tidyverse)

airquality

ggplot(data = airquality,aes(y=Wind,x=Temp))+geom_point()
```

```{r airquality-hint}
geom_point()+geom_smooth()
```

### Exercise 4

*You can include any number of single or multiple choice questions as a quiz. Use the `question` function to define a question and the `quiz` function for grouping multiple questions together.*

Some questions to verify your understandings:

```{r quiz}
quiz(
  question("What are the basic units in the grammar of graphics?",
    answer("Data and layers"),
    answer("Geometries and data"),
    answer("The data, the aesthetics, and the geometries", correct = TRUE),
    answer("Aesthetics and geometries")
  )
)
```

## Advanced

### Exercise 5
*Let's discover multiplot Can we draw it using R?*

For iris dataset, form a multiplot. Should we use facet_wrap? or facet_grid? Try to run the code and check.

```{r Multiplotgrid, exercise=TRUE}
#Facet_grid
library(tidyverse)
iris
ggplot(data = iris,aes(x=Sepal.Length))+geom_histogram(binwidth = 0.1) + facet_grid(Species~.)

```

```{r multiplotwrap, exercise = TRUE}
library(tidyverse)
iris
ggplot(data = iris,aes(x=Sepal.Length))+geom_histogram(binwidth = 0.1) + facet_wrap(~Species)

```