---
title: "Hadleyr4DS 3.1-3.3"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```


## Easy Level

### Exercise 1

*Here's a simple exercise with an empty code chunk provided for entering the answer.*

After installing Tidyverse package, given the mpg dataset, plot a scatterplot between any two continuous variable:
**Hint** : *To know what variables are write ?mpg*

```{r two-plus-two, exercise=TRUE}
library(tidyverse)
```

### Exercise 2

*Here's an exercise in which you are supposed to ammend the code so that it doesn't show error*

Correct the code and change the color aesthetics to alpha aesthetics mapping it with class attribute:
**HINT**: *print x to view the graph*

```{r add-function, exercise=TRUE, exercise.lines = 5}

library(tidyverse)
x <- ggplot(data = mpg) 
+ geom_point(mapping = aes(x = displ, y = hwy, color = red))

```

##  Intermediate Level

### Exercise 3

*Here's an exercise where you would need to apply what you learned. We also add a "hint" to the correct solution via the chunk immediate below labeled `print-limit-hint`.*

Modify the following code so that the legends of the aesthetics is not shown:

```{r print-limit, exercise=TRUE, exercise.eval=TRUE}
# Horizontal Legend box
library(tidyverse)
x <- ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = class))
```

```{r print-limit-hint}
show.legend
```

### Exercise 4

*You can include any number of single or multiple choice questions as a quiz. Use the `question` function to define a question and the `quiz` function for grouping multiple questions together.*

Question to verify that one has understood the basics of ggplot:

```{r quiz}
quiz(
  question("Which of the following modifies a ggplot or theme object by adding on new components?",
    answer("+.gg",correct = TRUE),
    answer("-.gg"),
    answer("/.gg"),
    answer(".gg")
  )
)
```

## Advanced

*Here's an exercise which requires a bit of brain storming. There will be some hints provided as well.*

### Exercise 5
Let's do some visualization with the basic knowledge. Questions will be in steps:

Step 1: Find the number of rows and columns of the dataset.

Step 2: Find the table of manufacturers.
**Hint**:*Use table()
and then index the attribute you want to show ($)*

Step 3: Make a bar chart to represent the number of manufacturers.
**Hint**: *geom can take point, smooth, bar etc.*

```{r Step1, exercise=TRUE, exercise.eval=TRUE}

```

### Aditional Challenge
*This is just an additional challenge question using the Iris dataset.*
There will be some hints to do this question.

## Additional Exercise
Make a 3D scatterplot to analyse the relation between sepal length, sepal width and petal length.
```{r Challenge, exercise=TRUE,exercise.eval = TRUE}
#install.packages("plot3D")
library("plot3D")
library(tidyverse)
```

```{r Challenge-hint}
#Step1 data(iris) & head()
#Step2 Define x,y, and z coordinates. For example, x<- sep.l <-iris$Sepal.Length
#Step3 use scatter3D(x,y,z,clab = c("Sepal","Width(cm)"))
```